\appendix
\section{Artifact Appendix}

\subsection{Abstract}
The artifact provides the paper-relevant MBPriorQ software, WikiText2 and
downstream experiment drivers, low-memory model execution, and curated MBPriorQ
accelerator sources in SpinalHDL. The public workflows reproduce the core W4A4
accuracy row, expose the 16-model and revised 19-model PPL matrices, cover both
models in the central ablations, and validate full-GPU/streamed equivalence.
Open simulation functionally exercises metadata handling, regular/refined
MultiMSA, the shared FPU pool, output synchronization, and packetization.
Commercial EDA data and reproductions of comparison methods are intentionally
outside the artifact scope.

\subsection{Artifact Check-list (Meta-information)}
{\small
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}
  \item \textbf{Algorithm:} MBPriorQ W4A4 fake quantization, online activation
    prior, selective 16-to-4 refinement, and EBW accounting.
  \item \textbf{Program:} Python/PyTorch software; Scala/SpinalHDL hardware;
    Bash/Python automated validation.
  \item \textbf{Model/data:} public paper-listed models, WikiText2, GSM8K,
    MMLU, and MMLU-Pro; only the Qwen3-0.6B importance matrix is included.
  \item \textbf{Run-time environment:} Linux x86-64; Python 3.12, PyTorch 2.10,
    Transformers 4.57; Java 17, sbt 1.10.2, SpinalHDL 1.8, Verilator 4.034+.
  \item \textbf{Hardware:} core PPL: NVIDIA GPU with at least 8\,GB free VRAM;
    large-model PPL: one decoder layer must fit VRAM; simulation: CPU only.
  \item \textbf{Metrics/output:} perplexity, effective bit width, cycle counts,
    and generated protocol CSVs.
  \item \textbf{Disk/time:} about 10\,GB for the core workflow; under 1 minute
    for smoke, tens of minutes for core experiments, and 8--15 minutes for the
    public hardware top. Multi-model runs require their public checkpoints and
    range from hours to days.
  \item \textbf{Availability:} tagged release \ArtifactVersion; DOI
    \ArtifactDOI; source license \ArtifactLicense.
\end{itemize}
}

\subsection{Description}
\subsubsection{How to Access}
The immutable artifact is distributed through the DOI above. The evaluated Git
tag and archive version must match. The repository root \path{README.md}
indexes the claim map, provenance, expected outputs, and release checksums.

\subsubsection{Hardware, Software, Data, and Models}
The tensor check needs a Linux host with approximately 8\,GB RAM. The core PPL
run needs 16\,GB system RAM and 8\,GB free CUDA VRAM. Large models use
safetensors layer streaming with CPU-resident hidden windows; the full model
does not need to fit VRAM. Open hardware simulation additionally requires Java
17, sbt, Verilator, Make, and a C++ compiler. Conda specifications are in
\path{environment/}. Models and datasets are obtained from their public
providers; neither is redistributed.

\subsection{Installation}
From the repository root, create the software environment with:
\begin{quote}\small\ttfamily
conda env create -f environment/software.yml\\
conda activate mbpriorq-ae\\
python -m pip install -e software
\end{quote}
For RTL, follow \path{environment/README.md} to create the hardware environment
and install sbt 1.10.2. Installation takes about 10--20 minutes with a normal
package cache and Internet connection.

\subsection{Experiment Workflow}
Download Qwen3-0.6B and WikiText2 for the core path. Additional workflows state
their model and dataset variables in their local README. Run from the root:
{\scriptsize
\begin{flushleft}\setlength\parskip{0pt}
1. \path{scripts/run_smoke.sh}\\
2. \path{experiments/core_accuracy/run.sh}\\
3. \path{experiments/model_family_ppl/run_paper16.sh}\\
4. \path{experiments/downstream_benchmarks/run.sh}\\
5a. \path{experiments/activation_attribution/run.sh}\\
5b. \path{experiments/granularity_ablation/run.sh}\\
6. \path{experiments/offload_equivalence/run.sh}\\
7. \path{scripts/run_hardware_all.sh}
\end{flushleft}
}
Step 1 checks tensor/EBW semantics. Step 2 is the bounded Results Reproduced
target. Steps 3--5 are long model/table extensions; both ablations include
Qwen3-0.6B and Llama2-7B. Step 6 checks that streaming does not shift NLL.
Step 7 validates actual SpinalHDL modules and the public 1024-bit packet top.

\subsection{Evaluation and Expected Results}
The full core run must process 146 contiguous 2048-token windows and report:
\begin{center}
\small
\begin{tabular}{lrr}
\toprule
Method & PPL & Act. EBW \\
\midrule
BF16 & 20.9240 & -- \\
W4A4 MBPriorQ & 24.2289 & 4.994211 \\
\bottomrule
\end{tabular}
\end{center}
For Qwen3-0.6B, expected PPL is 24.8590 at 16-to-8, 24.2289 at 16-to-4,
and 23.9532 at 16-to-2. Corresponding activation EBW is 4.704345,
4.994211, and 5.613351. Llama2-7B and other expectations are stored beside
their drivers. Full scripts enforce recorded tolerances and sample counts;
quick scripts check execution only. Hardware checks reproduce expected CSVs.

\subsection{Experiment Customization}
\texttt{NUM\_SAMPLES} shortens PPL runs; only zero (all windows) is a full row.
\texttt{MODEL\_ROOTS} or a JSON path map locates the 16/19 model suite.
Qwen3-0.6B alone consumes the included imatrix. Hardware module tests may be
run separately from the heavier public-top compilation.

\subsection{Notes}
The complete model matrix is executable but remains an extended run because of
public model access, hundreds of GB of storage, and day-scale quantization for
the largest entry. The default Results Reproduced target is the fully
executable Qwen3-0.6B workflow. Hardware tests target functionality, not
speedup, area, or power. Comparison-method code and commercial synthesis
evidence are not distributed or evaluated.

\subsection{Methodology}
Artifact review and badging follow the ACM policy at
\url{https://www.acm.org/publications/policies/artifact-review-and-badging-current}
and the cTuning AE methodology at \url{https://ctuning.org/ae}.
